\textbf{NBA Party}

### 2017-04-06 init_model.rnw
Stratified random sampling to estimate last-location fixed effects. These are then used as features in a second stage model, which achieves very significant results.

<<echo=F,results='hide'>>=
require(data.table)
require(ggplot2)
load(file = 'tmp_data/covers_lines.RData')
lines[, `:=`(pct = NULL, weekend = NULL)]
others <- grep("party", names(lines), value = T, invert = T)
setcolorder(lines, c(others, c('party')))
@

@@

model <- glm(outcome == 'W' ~ party + ndays.lgame + I(log(travel.dist+1)) + season,
             data = lines, family = 'binomial', subset = season < 2016)

@@

<<>>=
### We're only interested in making predictions when teams party.
yhat <- predict(model, newdata = lines[season >= 2016 & party == 1], type = 'response')
yhat <- ifelse(yhat < 0.41325, 0, 1) # We use a simple threshold based on hist(yhat).
table(yhat, lines[season >= 2016 & party == 1, outcome])
@

>>>>

<<echo=F,results='hide'>>=
require(data.table)
require(ggplot2)
load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/ndrink_estabs.RData')
drinks[, county := NULL]

lines[, `:=`(pct = NULL, weekend = NULL)]

### We're careful to merge in ndrinking_estabs according to the PREV game played.
lines <- merge(lines, drinks, 
               by.x = c('last.game.loc', 'season'), 
               by.y = c('team',          'season'))
setkey(lines, date)
others <- grep("(party)|(last.game)", names(lines), value = T, invert = T)
setcolorder(lines, c(others, c('last.game.loc', 'party')))

require(sampling)
set.seed(04052017)
setkey(lines, season, last.game.loc)

n = length(unique(lines$last.game.loc))
m = length(unique(lines$season))
s = strata(data = lines, stratanames = c('season', 'last.game.loc'),
           size = rep(5, n*m), method = 'srswor')

var.creation.indices = s$ID_unit
var.creation = lines[var.creation.indices]
training     = lines[-var.creation.indices]

m = glm(outcome == 'W' ~ 0 + last.game.loc, data = var.creation, family = 'binomial')
coef <- m$coef
names(coef) <- gsub('last.game.loc', '', names(coef))
coef = data.table(last.game.loc = names(coef), coef)

setkey(training, last.game.loc)
training = training[coef]

m = glm(outcome == 'W' ~ I(coef*(ndays.lgame==1)), data = training, family = 'binomial', subset = season < 2017) # Significant.

### Not quite worth betting on, yet.
yhat <- predict(m, newdata = training[season >= 2017 & ndays.lgame == 1], type = 'response')
yhat <- ifelse(yhat < 0.519, 0, 1)
table(yhat, training[season >= 2017 & ndays.lgame==1, outcome])

@@

model <- glm(outcome == 'W' ~ party + ndays.lgame + I(log(travel.dist+1)) + 
                 season + nmusicians,
             data = lines, family = 'binomial', subset = season < 2016)

@@

<<>>=
### We're only interested in making predictions when teams party. When they do, we bet against them.
yhat <- predict(model, newdata = lines[season >= 2016 & party == 1], type = 'response')
yhat <- ifelse(yhat < 0.41325, 0, 1) # We use a simple threshold based on hist(yhat).
table(yhat, lines[season >= 2016 & party == 1, outcome])
@
